### 2024-11-14 uw-ethesis-frontpgs.tex
new

        \Huge
        {\bf Resilient Machine Learning Approaches to Risk Evaluation and Hedging in Financial Portfolios and Variable Annuities}

@@

I would like to thank Professor Mingbin Feng and Professor Tony Wirjanto for their valuable support. They have patiently helped me through my journey as a Ph.D. student.  
\cleardoublepage

>>>>

        \Huge
        {\bf Resilient Machine Learning Approaches for Fast Risk Evaluation and Management in Financial Portfolios and Variable Annuities}

@@

I would like to thank Professor Mingbin Feng and Professor Tony Wirjanto for their valuable support. 
They have patiently helped me through my research journey.
I am forever grateful for my true best friends, who have supported me during the most difficult times.
